Drivers of spatial synchrony in giant kelp populations

### 2021-05-02 paper/SupMat.Rnw
moving files

\usepackage{Sweave}
\begin{document}
\input{SupMat-concordance}

%The following is where you load in the numeric results that will be embedded in the text

@@

Noise with symmetric tail association was generated by taking a very large sample (100000) of left-tail associated noise, as described above, and then calculating the Pearson correaltion coefficient, rho. The value obtained was ... . The symmetric noise was then generated once from $N(\begin{pmatrix} 0\\0\end{pmatrix}, \Sigma)$ where $\Sigma = \begin{pmatrix} 1&\rho \\ \rho&1\end{pmatrix}$, denoting the points so generated by $(\tilde b_1^{(i)},\tilde b_2^{(i)})$ for $i=1,...,M$. We then set $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)}+ \mu_2$.

@@

\begin{align}
\bar r_1 &= \EX(\ln[1-\delta+\delta \exp(\beta_1-\eta-(\beta_2-\eta))])\\
&= \EX(\ln[1-\delta+\delta \exp(\beta_1-\beta_2)]).
\end{align}
\noindent And so altering the mean of both $b_1$ and $b_2$ distributions by the same amount has no affect of $\bar r_1$, and thus $\bar r_1$ in the asymmetric tail associations also depends only on $\mu_1 - \mu_2$ and not independtly on $\mu_1$ or $\mu_2$.

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

%The following is where you load in the numeric results that will be embedded in the text
<<eval=T,echo=F,message=F,warning=F>>=
#place R code here for loading in necessary variables from Results
@

@@

Noise with symmetric tail association was generated by taking a very large sample (1000?) of left-tail associated noise, as described above, and then calculating the Pearson correaltion coefficient, rho. The value obtained was ... . The symmetric noise was then generated once from $N(\begin{pmatrix} 0\\0\end{pmatrix}, \Sigma)$ where $\Sigma = \begin{pmatrix} 1&\rho \\ \rho&1\end{pmatrix}$, denoting the points so generated by $(\tilde b_1^{(i)},\tilde b_2^{(i)})$ for $i=1,...,M$. We then set $b_1^{(i)} = \sigma \tilde b_1^{(i)} + \mu_1$ and $b_2^{(i)} = \sigma \tilde b_2^{(i)}+ \mu_2$.

@@

\begin{align}
\bar r_1 &= \EX(\ln[1-\delta+\delta \exp(\beta_1-\eta-(\beta_2-\eta))])\\
&= \EX(\ln[1-\delta+\delta \exp(\beta_1-\beta_2)]).
\end{align}
\noindent And so altering the mean of both $b_1$ and $b_2$ distributions by the same amount has no affect of $\bar r_1$ in the asymmetric tail associations. Also ? depends only on $\mu_1 - \mu_2$ and not independtly on $\mu_1$ or $\mu_2$.
